---
title: "LiveSessionAssignment11"
author: "Daniel Higdon (MSDS 6306 - 404)"
date: "3/27/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
I have filled in all of the "TODO" sections below. My GitHub repository can be found here: <https://github.com/dmhigdon/DDS-HW11>.


## Coding Section
Pleaes note, to make the document more readable I have broken up the code into chunks.

### Loading the package
```{r code}
### Uncomment and install packages if you don't have it
####install.packages("tseries")

library(tseries)
```

### Downloading the data
```{r code1}
### S&P 500 (^GSPC)
###    SNP - SNP Real Time Price. Currency in USD
### TODO: Download the data of SP500 '^gspc'.
SNPdata <- get.hist.quote('^gspc',quote="Close")
```

### Calculating the log returns and volatility (includes creating the getVol function)
```{r code2}
### TODO: Calculate the log returns, which is the subtractration of log(lag(SNPdata)) and log(SNPdata)
SNPret <- log(lag(SNPdata)) - log(SNPdata)

### TODO: Calculate volatility measure that is to multiply sd(SNPret),sqrt(250), 100
SNPvol <- sd(SNPret)*sqrt(250)*100

### Define getVol function for volatility
getVol <- function(d, logrets) {
  var = 0
  lam = 0
  varlist <- c()
  
  for (r in logrets) {
    lam = lam*(1 - 1/d) + 1
    var = (1 - 1/lam)*var + (1/lam)*r^2
    varlist <- c(varlist, var)
  }
  
  sqrt(varlist)
}
```

### Calculating volatility with three different decay factors
```{r code3}
## Calculate volatility over entire length of series for various three different decay factors: 10 30. 100

### TODO: call getVol function with the parameters: 10,SNPret
volest <- getVol(10,SNPret)

### TODO: call getVol function with the parameters: 30,SNPret
volest2 <- getVol(30,SNPret)

### TODO: call getVol function with the parameters: 100,SNPret
volest3 <- getVol(100,SNPret)
```
### Plotting the results
```{r code4}
## Plot the results, overlaying the volatility curves on the data, just as was done in the S&P example.
plot(volest,type="l")

### TODO: Add connected line segments for volest2 with the parameters: type="l",col="red"
### hint: look at oilExerciseCode.R file at the live discussion
lines(volest2,col="red", type="l")

### TODO: Add connected line segments for volest3 with the parameters: type="l",col="blue"
lines(volest3,col="blue", type="l")
```